```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Solutions

The solutions will appear below when you fill the "Show solutions?" checkbox.

```{r eval = .flexteach_solutions, echo=FALSE}
plot(.flexteach_info$data)
```



```{r eval = TRUE, echo = FALSE}
library(reactR)
library(htmltools)

browsable(tagList(
        tags$div(id = "app"),
        tags$script(
                "
                  ReactDOM.render(
                    React.createElement(
                      'p',
                      null,
                      'Powered by React'
                    ),
                    document.getElementById('app')
                  )
                "
        ),
        #add core-js first to work in RStudio Viewer
        #html_dependency_corejs(),
        html_dependency_react()
))
```


\[
y \sim \mbox{Normal}(0,1)
\]


<a id="test2-button" class="btn btn-default" target="_blank">
  <i class="fa fa-file-download" role="presentation" aria-label="file-download icon"></i>
    Download your responses
</a>


What is 39+22? <input id='test2-input-q1'/>

What is 34 / 2? <input id='test2-input-q2'/>

<div id="drop-region-q3" class="drop-region">
  <div class="drop-message">
<p>Drag image of SPSS output/click to upload<br/>Click image to delete</p>
  </div>
  <div class="image-preview"></div>
</div>


